---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(vembedr); library(htmltools); library(leaflet)
```

<link rel="stylesheet" href="styles.css" type="text/css">

<style type="text/css">
body{ /* Normal  */ font-size: 16px; font-family: Arial; color:black}
td {  /* Table  */ font-size: 8px;}
h1.title {font-size: 38px; color: DarkRed;}
h1 { /* Header 1 */ font-size: 28px; color: Black;}
h2 { /* Header 2 */ font-size: 22px; color: Black;}
h3 { /* Header 3 */ font-size: 18px; color: Black;}
code.r{ /* Code block */ font-size: 12px;}
pre { /* Code block - determines code spacing between lines */ font-size: 14px;}
</style>

# Fieldwork

Here are sites where my colleagues and I have developed field research projects. The map is still under-construction; check back in the future for project descriptions and pictures.

```{r leaflet, echo=FALSE}

df <- read.csv(textConnection(
"Name,Lat,Long,
Conecuh National Forest, 34.597131,-89.000,
Yunnan China, 22.000, 100.8000,
Lower Canyons TX, 29.633241, -102.74,
Painter Gap GA, 34.799517, -84.576,
Spring Creek GA, 30.937477, -84.7426,
Mobile Bay AL, 30.868031, -87.9411,
La Selva Biological Station, 10.425307, -84.017,
Palo Verde Biological Station, 10.296803, -85.273"
))

leaflet(df) %>% addTiles() %>%
  addMarkers(~Long, ~Lat, popup = ~htmlEscape(Name)) %>%
  addProviderTiles(providers$OpenMapSurfer.Roads)

```

Here are videos from some favorite field excursions - for research or just for fun.  

```{r library(vembedr), echo=FALSE}
embed_vimeo("152795925")

embed_vimeo("291925447")

embed_vimeo("491806654")

embed_vimeo("574933065")
```
